Applying Automated Verification to Optimal Sizing of Stand-alone Solar Photovoltaic Systems\\

### 2019-04-24 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
updated text ASE

\begin{abstract}
Software verification has experienced significant progress over the last two decades. Currently, there exist various software verifies that are able to solve intricate real-world problems, e.g., to design and verify renewable and stand-alone solar photovoltaic (PV) systems. 
Currently around $1$ billion of people do not have electrical energy; energy poverty alleviation has become an important political issue. 
%Several initiatives and policies have been proposed to deal with poor access to sources of energy in many developing countries. 
Particular attention is given to renewables and PV systems. Unfortunately, existing tools available to evaluate PV designs are mainly based on simulations that do not cover all aspects of the design space. 
The use of automated verification in PV systems is a recent subject with only a few initiatives. 
Here we develop an optimization algorithm and report its preliminary results using four state-of-art software verifiers to optimize the sizing of a PV system, where commercial equipment data is part of the specification and the technical solution is conjugated with the financial analysis of the obtained sizing. 
Our proposal is unprecedented and interesting to streamline the design and analysis of PV systems. Experimental results show that \textcolor{red}{we should describe here a summary of the results}.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textcolor{red}{What is the relation of this paper with software engineering (SE)?}

@@

Formal methods based on \textit{model checking} can offer a great potential to obtain a more effective design process of PV systems~\cite{ClarkeHV18}. In this study, we review verification tools and related them to design and verify PV systems, which was uncommon in prior studies~\cite{abs-1811-09438}.

@@

\label{sec:AutomatedVerification}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw. Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored, and questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}. Here we evaluate four state-of-the-art model checkers to formally optimize the sizing of PV designs w.r.t. user requirements.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Ultimate Automizer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Ultimate Automizer is an automatic software verification tool for C programs that is able to check safety and liveness properties. The tool implements an automata-based instance of the Counterexample-Guides Abstraction Refinement (CEGAR) scheme. CEGAR is a technique that iteratively refines an abstract model using counterexamples and use three concepts: precision, feasibility check and refinement~\cite{CEGAR}. In each iteration, Automizer picks a trace (sequence of statements) that leads from the initial location to the error location and check whether the trace is feasible or infeasible. If the trace is feasible, an error is reported to the user; otherwise it is computed a sequence of predicates along the trace as a proof of the trace's infeasibility. The predicates are a sequence of interpolants since each predicate "interpolates" between a set of reachable states and a set of states from which it cannot reach the error. In the refinement step of the CEGAR loop, Automizer tries to find all traces whose infeasibility can be shown with the given predicates and subtract these traces from the set of (potentially spurious) error traces that have not yet been analyzed. It is used automata to represent sets of traces. The difference to a classical CEGAR-based predicate abstraction is that Automizer has to do any logical reasoning (e.g., SMT solver calls) that involves predicates of different CEGAR iterations~\cite{Automizer2018}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{CPAchecker}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Automatic program verification requires a choice between precision and efficiency. The
more precise a method, the fewer false positives it will produce, but also the more expensive it is, and thus applicable to fewer programs. Historically, this trade-off was
reflected in two major approaches to static verification: program analysis and model
checking. In order to experiment with the trade-off, and in order to be able to set the dial between the two extreme points, Configurable Program Analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting. The CPA formalism provides an interface for the definition of program analyses. Consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework. The comparison among different approaches in the same experimental setting is intended to be easy and the experimental results are expected to be more meaningful~\cite{Beyer2011}. Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges. The CPA framework provides interfaces to SMT solvers and interpolation procedures~\cite{Beyer2011}. Currently, CPAchecker uses MathSAT as SMT solver; and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.

@@

We have performed two case studies to evaluate the proposed approach of optimization as described in Table~\ref{tab1}. Furthermore, four start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification}: CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}, UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, were used to compare the approach effectiveness and efficiency. The case studies are related to a stand-alone PV system with the specifications shown in Table~\ref{tab1}.

@@

%used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
\begin{table}
\caption{Case studies and Results: optimization of PV systems.}\label{tab1}
\begin{scriptsize}
\begin{tabular}{|c|c|c|}
\hline
\hline
 & Case 1 & Case 2\\
\hline
\hline
Tool & \makecell{Demand = 501W \\ Peak = 501W \\ Energy=3900Wh/day \\ Battery autonomy=48h} & \makecell{Demand = 915W \\ Peak = 980W \\ Energy=4880Wh/day \\ Battery autonomy=6h}\\
\hline
CBMC 5.11 (MiniSat 2.2.1) & Out of Memory & Out of Memory \\
\hline
ESBMC 6.0.0 (Boolector 3.0.1) & Timeout & Timeout \\
\hline
UAutomizer 0.1.24 (Z3 4.8.3) & UNKNOWN & UNKNOWN \\
\hline
CPAchecker 1.8 (MathSAT 5.5.3) & SAT (65 minutes) & x4 \\
\hline
\hline
\end{tabular}
\end{scriptsize}
\end{table}

>>>>

\begin{abstract}
Software verification has experienced significant progress over the last two decades. Currently, there exist various software verifies that are able to solve intricate real-world problems, e.g., to design and verify renewable and stand-alone solar photovoltaic (PV) systems. 
Currently around $1$ billion of people do not have electrical energy; energy poverty alleviation has become an important political issue. 
%Several initiatives and policies have been proposed to deal with poor access to sources of energy in many developing countries. 
Particular attention is given to renewables and PV systems. Unfortunately, existing tools available to evaluate PV designs are mainly based on simulations that do not cover all aspects of the design space. 
The use of automated verification in PV systems is a recent subject with only a few initiatives. 
Here we develop an optimization algorithm and report its preliminary results using three state-of-art software verifiers to optimize the sizing of a PV system, where commercial equipment data is part of the specification and the technical solution is conjugated with the financial analysis of the obtained sizing. 
Our proposal is unprecedented and interesting to streamline the design and analysis of PV systems. Experimental results show that \textcolor{red}{we should describe here a summary of the results}.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Cyber-Physical  Systems  (CPS)  are  “engineered systems  that  are built from, and depend upon, the seamless integration of computational  and  physical  components”~\cite{NSF2015}. During operation, such components must frequently adapt to the executing environment changes faced at run-time (dynamics of the physical processes) and must be able to continue to behave in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}. %Important quality aspects for CPS include scalability, e.g., ensuring that CPS applications can scale to urban-wide deployment environments [Nessi].

While some research efforts exist to enhance and optimize the software development processes for CPS, more investigation and discussion of better and more effective models is needed [Al-Jaroodi]. Among the opportunities for enhancements there is the developing new techniques and tools to support CPS requirements gathering and analysis. The developed techniques need to be able to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS. In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}. Uncertainty and variability, at the same time, can be dealed with formal verification~\cite{NESSI}. Energy production, distribution, and optimization are all CPS problems~\cite{UC}.

@@

Formal methods based on \textit{model checking} can offer a great potential to obtain a more effective design process of systems~\cite{ClarkeHV18}. Therefore, in the context of this proposal, a cyber-physical system, specifically a PV system, is the target. We review verification tools and related them to design and to verify PV systems, which was uncommon in prior studies~\cite{abs-1811-09438}.

@@

\label{sec:AutomatedVerification}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw. Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored, and questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}. Here we evaluate three state-of-the-art model checkers to formally optimize the sizing of PV designs w.r.t. user requirements.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsection{Ultimate Automizer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Ultimate Automizer is an automatic software verification tool for C programs that is able to check safety and liveness properties. The tool implements an automata-based instance of the Counterexample-Guides Abstraction Refinement (CEGAR) scheme. CEGAR is a technique that iteratively refines an abstract model using counterexamples and use three concepts: precision, feasibility check and refinement~\cite{CEGAR}. In each iteration, Automizer picks a trace (sequence of statements) that leads from the initial location to the error location and check whether the trace is feasible or infeasible. If the trace is feasible, an error is reported to the user; otherwise it is computed a sequence of predicates along the trace as a proof of the trace's infeasibility. The predicates are a sequence of interpolants since each predicate "interpolates" between a set of reachable states and a set of states from which it cannot reach the error. In the refinement step of the CEGAR loop, Automizer tries to find all traces whose infeasibility can be shown with the given predicates and subtract these traces from the set of (potentially spurious) error traces that have not yet been analyzed. It is used automata to represent sets of traces. The difference to a classical CEGAR-based predicate abstraction is that Automizer has to do any logical reasoning (e.g., SMT solver calls) that involves predicates of different CEGAR iterations~\cite{Automizer2018}. 
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{CPAchecker}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Automatic program verification requires a choice between precision and efficiency. The
more precise a method, the fewer false positives it will produce, but also the more expensive it is, and thus applicable to fewer programs. Historically, this trade-off was
reflected in two major approaches to static verification: program analysis and model
checking. In order to experiment with the trade-off, and in order to be able to set the dial between the two extreme points, Configurable Program Analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting. The CPA formalism provides an interface for the definition of program analyses. Consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework. The comparison among different approaches in the same experimental setting is intended to be easy and the experimental results are expected to be more meaningful~\cite{Beyer2011}. Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges. The CPA framework provides interfaces to SMT solvers and interpolation procedures~\cite{Beyer2011}. Currently, CPAchecker uses MathSAT as SMT solver; and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}.

@@

We have performed two case studies to evaluate the proposed approach of optimization as described in Table~\ref{tab1}. Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification}: CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, 
and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, were used to compare the approach effectiveness and efficiency. The case studies are related to a stand-alone PV system with the specifications shown in Table~\ref{tab1}.

@@

%used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
\begin{table}
\caption{Case studies and Results: optimization of PV systems.}\label{tab1}
\begin{scriptsize}
\begin{tabular}{|c|c|c|}
\hline
\hline
 & Case 1 & Case 2\\
\hline
\hline
Tool & \makecell{Demand = 501W \\ Peak = 501W \\ Energy=3900Wh/day \\ Battery autonomy=48h} & \makecell{Demand = 915W \\ Peak = 980W \\ Energy=4880Wh/day \\ Battery autonomy=6h}\\
\hline
CBMC 5.11 (MiniSat 2.2.1) & Out of Memory & Out of Memory \\
\hline
ESBMC 6.0.0 (Boolector 3.0.1) & Timeout & Timeout \\
\hline
%UAutomizer 0.1.24 (Z3 4.8.3) & UNKNOWN & UNKNOWN \\
%\hline
CPAchecker 1.8 (MathSAT 5.5.3) & SAT (65 minutes) & x4 \\
\hline
\hline
\end{tabular}
\end{scriptsize}
\end{table}
